---
title: "Prepare for frequentist approach"
subtitle: "Last updated `r Sys.Date()`"
author: "Artemis Koukounari, Matt Secrest (alphabetical)"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    keep_md: FALSE
---

```{r setup,include = FALSE}
knitr::opts_chunk$set(eval = TRUE,         # Evaluate code
                      echo = FALSE,         # echo code?
                      message = FALSE,     # Show messages
                      warning = FALSE,     # Show warnings
                      fig.width = 12,       # Default plot width
                      fig.height = 8,      # .... height
                      dpi = 300,           # Plot resolution
                      fig.align = "left")  # Figure alignment 
```



## Cox PH results{.tabset .tabset-pills .tabset-fade}

### MORPHEUS only

```{r}
summary(morpheus_only_cox)


morpheus_only_km[[2]] %>% 
  gt() %>% 
  fmt_number(columns = 5:10,decimals = 3)

morpheus_only_km[[3]]
```

### MORPHEUS + all eligible RWD atezo patients only

```{r}
summary(combined_full_cox)

combined_full_km[[2]] %>% 
  gt() %>% 
  fmt_number(columns = 5:10,decimals = 3)

combined_full_km[[3]]
```


## Matching exploration {.tabset .tabset-pills .tabset-fade}

Based on the results below, it was decided to pursue 1:1 propensity score matching 
using a propensity score model adjusted for:

* sex
* ecog
* bmi
* age
* tobhx
* surgery
* viscfl

### Full matching{.tabset .tabset-pills .tabset-fade}

```{r, results = 'asis'}
for(i in 1:NROW(full_matches)){
  pander::pandoc.header(paste0(full_matches[[i]]$`adjustment vars`,collapse=', '),level=4)
  pander::pandoc.p(paste0(full_matches[[i]]$`n patients dropped with missing values`, 
                          ' patients dropped with missing values.'))
  summary(full_matches[[i]][[4]])$nn %>% 
    as_tibble(rownames = ' ') %>% 
    kableExtra::kable() %>% 
    kableExtra::kable_styling() %>% 
    print()
  print(full_matches[[i]]$plot)
  pander::pandoc.p('')
  pander::pandoc.p('')
  
}

```

### 1:1 greedy nearest-neighbor PS matching {.tabset .tabset-pills .tabset-fade}

```{r, results = 'asis'}
for(i in 1:NROW(greedy_matches)){
  pander::pandoc.header(paste0(greedy_matches[[i]]$`adjustment vars`,collapse=', '),level=4)
  pander::pandoc.p(paste0(greedy_matches[[i]]$`n patients dropped with missing values`, 
                          ' patients dropped with missing values. ',
                          NROW(match.data(greedy_matches[[i]]$`matchit object`)),
                          ' left after matching'))
  summary(greedy_matches[[i]][[4]])$nn %>% 
    as_tibble(rownames = ' ') %>% 
    kableExtra::kable() %>% 
    kableExtra::kable_styling() %>% 
    print()
  print(greedy_matches[[i]]$plot)
  pander::pandoc.p('')
  pander::pandoc.p('')
  
}

```


### Exact matching {.tabset .tabset-pills .tabset-fade}

```{r, results = 'asis'}
for(i in 1:NROW(exact_matches)){
  pander::pandoc.header(paste0(exact_matches[[i]]$`adjustment vars`,collapse=', '),level=4)
  pander::pandoc.p(paste0(exact_matches[[i]]$`n patients dropped with missing values`, 
                          ' patients dropped with missing values. ',
                          NROW(match.data(greedy_matches[[i]]$`matchit object`)),
                          ' left after matching'))
  summary(exact_matches[[i]][[4]])$nn %>% 
    as_tibble(rownames = ' ') %>% 
    kableExtra::kable() %>% 
    kableExtra::kable_styling() %>% 
    print()
  print(exact_matches[[i]]$plot)
  pander::pandoc.p('')
  pander::pandoc.p('')
  
}

```


## Explore parametric modeling - MORPHEUS population only{.tabset .tabset-pills .tabset-fade}

### Exponential

```{r}
just_trial_parametric[['Exponential']][[1]]
just_trial_parametric[['Exponential']][[2]]()
just_trial_parametric[['Exponential']][[3]]
```

### Weibull

```{r}
just_trial_parametric[['Weibull']][[1]]
just_trial_parametric[['Weibull']][[2]]()
just_trial_parametric[['Weibull']][[3]]
```

### Gompertz

```{r}
just_trial_parametric[['Gompertz']][[1]]
just_trial_parametric[['Gompertz']][[2]]()
just_trial_parametric[['Gompertz']][[3]]
```


## Explore parametric modeling - MORPHEUS + full Flatiron RWD population{.tabset .tabset-pills .tabset-fade}

### Exponential

```{r}
full_pop_parametric[['Exponential']][[1]]
full_pop_parametric[['Exponential']][[2]]()
full_pop_parametric[['Exponential']][[3]]
```

### Weibull

```{r}
full_pop_parametric[['Weibull']][[1]]
full_pop_parametric[['Weibull']][[2]]()
full_pop_parametric[['Weibull']][[3]]
```

### Gompertz

```{r}
full_pop_parametric[['Gompertz']][[1]]
full_pop_parametric[['Gompertz']][[2]]()
full_pop_parametric[['Gompertz']][[3]]
```

