---
title: "Frequentist results"
subtitle: "Last updated `r Sys.Date()`"
author: "Artemis Koukounari, Matt Secrest (alphabetical)"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    keep_md: FALSE
---

```{r setup,include = FALSE}
knitr::opts_chunk$set(eval = TRUE,         # Evaluate code
                      echo = FALSE,         # echo code?
                      message = FALSE,     # Show messages
                      warning = FALSE,     # Show warnings
                      fig.width = 12,       # Default plot width
                      fig.height = 8,      # .... height
                      dpi = 300,           # Plot resolution
                      fig.align = "left")  # Figure alignment 
```

## 1:1 greedy nearest neighbor matching{.tabset .tabset-pills .tabset-fade}

1:1 propensity score matching using a propensity score model adjusted for:

* sex
* ecog
* bmi
* age
* tobhx
* surgery
* viscfl

### Cox proportional hazards{.tabset .tabset-pills .tabset-fade}

#### Results
```{r}
summary(combined_ps_match_cox)
```

#### KM curves
```{r}
combined_ps_match_km[[2]] %>% 
  gt() %>% 
  fmt_number(columns = 5:10,decimals = 3)

combined_ps_match_km[[3]]
```

### Parametric modeling results{.tabset .tabset-pills .tabset-fade}

#### Exponential{.tabset .tabset-pills .tabset-fade}

```{r}
ps_match_pop_parametric[['Exponential']][[1]]
ps_match_pop_parametric[['Exponential']][[2]]()
ps_match_pop_parametric[['Exponential']][[3]]
```

#### Weibull{.tabset .tabset-pills .tabset-fade}

```{r}
ps_match_pop_parametric[['Weibull']][[1]]
ps_match_pop_parametric[['Weibull']][[2]]()
ps_match_pop_parametric[['Weibull']][[3]]
```

#### Gompertz{.tabset .tabset-pills .tabset-fade}

```{r}
ps_match_pop_parametric[['Gompertz']][[1]]
ps_match_pop_parametric[['Gompertz']][[2]]()
ps_match_pop_parametric[['Gompertz']][[3]]
```


