---
title: "Bayesian Dynamic Borrowing results"
subtitle: "Last updated `r Sys.Date()`"
author: "Artemis Koukounari, Matt Secrest (alphabetical)"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    keep_md: FALSE
---

```{r setup,include = FALSE}
knitr::opts_chunk$set(eval = TRUE,         # Evaluate code
                      echo = FALSE,         # echo code?
                      message = FALSE,     # Show messages
                      warning = FALSE,     # Show warnings
                      fig.width = 12,       # Default plot width
                      fig.height = 8,      # .... height
                      dpi = 300,           # Plot resolution
                      fig.align = "left")  # Figure alignment 
```

## Summary of model features{.tabset .tabset-pills .tabset-fade}

### Model type

There are four families of models varying in distribution and the prior 
commensurability parameter, tau.

```{r, results = 'asis'}

knitr::kable(bdb_summary_models) %>% 
    kableExtra::kable_styling()

```

### Population

There are two populations evaluated.

```{r, results = 'asis'}

knitr::kable(bdb_summary_populations)%>% 
    kableExtra::kable_styling()

```

### Model parametrization (model type 1 only)

There are two populations evaluated.

```{r, results = 'asis'}

knitr::kable(bdb_model1_validation)%>% 
    kableExtra::kable_styling()

```

## JAGS code for different model types{.tabset .tabset-pills .tabset-fade}

### Model 1{.tabset .tabset-pills .tabset-fade}
weibull, tau ~ dgamma(0.001,0.001)

#### Parametrization I
2 alphas and 1 beta


```{r comment=''}
cat(readLines('~/R/PHC-1094/analysis/jags/model1_I'), sep = '\n')
```

#### Parametrization II
3 betas

```{r comment=''}
cat(readLines('~/R/PHC-1094/analysis/jags/model1_II'), sep = '\n')
```

#### Parametrization III
zeros method

```{r comment=''}
cat(readLines('~/R/PHC-1094/analysis/jags/model1_III'), sep = '\n')
```

#### Parametrization IV
iterating separately

```{r comment=''}
cat(readLines('~/R/PHC-1094/analysis/jags/model1_IV'), sep = '\n')
```

### Model 2

weibull, tau ~ dgamma(1,0.001)

```{r comment=''}
cat(readLines('~/R/PHC-1094/analysis/jags/model2'), sep = '\n')
```

### Model 3

exponential, tau ~ dgamma(0.001,0.001)

```{r comment=''}
cat(readLines('~/R/PHC-1094/analysis/jags/model3'), sep = '\n')
```


### Model 4

exponential, tau ~ dgamma(1,0.001)

```{r comment=''}
cat(readLines('~/R/PHC-1094/analysis/jags/model4'), sep = '\n')
```

## Results{.tabset .tabset-pills .tabset-fade}

### Population A (Flatiron atezo 1:1 PS matched population){.tabset .tabset-pills .tabset-fade}

#### Model 1{.tabset .tabset-pills .tabset-fade}

##### Parametrization I

```{r}
summary(hybrid_control_model_1_A_I_cs)
MCMCvis::MCMCtrace(hybrid_control_model_1_A_I_cs,
                   params=c('alpha','beta','tau'), 
                   type = 'density',
                   iter=990000,
                   pdf = F,
                   ISB=F,
                   ind = T)
MCMCvis::MCMCtrace(hybrid_control_model_1_A_I_cs,
                   params=c('alpha','beta','tau'), 
                   iter=990000,
                   type = 'trace',
                   pdf = F,
                   ISB=F,
                   ind = T)
```

##### Parametrization II

```{r}
summary(hybrid_control_model_1_A_II_cs)
MCMCvis::MCMCtrace(hybrid_control_model_1_A_II_cs,
                   params=c('alpha','beta','tau'), 
                   type = 'density',
                   iter=990000,
                   pdf = F,
                   ISB=F,
                   ind = T)
MCMCvis::MCMCtrace(hybrid_control_model_1_A_II_cs,
                   params=c('alpha','beta','tau'), 
                   iter=990000,
                   type = 'trace',
                   pdf = F,
                   ISB=F,
                   ind = T)
```

##### Parametrization III

```{r}
summary(hybrid_control_model_1_A_III_cs)
MCMCvis::MCMCtrace(hybrid_control_model_1_A_III_cs,
                   params=c('alpha','beta','tau'), 
                   type = 'density',
                   iter=990000,
                   pdf = F,
                   ISB=F,
                   ind = T)
MCMCvis::MCMCtrace(hybrid_control_model_1_A_III_cs,
                   params=c('alpha','beta','tau'), 
                   iter=990000,
                   type = 'trace',
                   pdf = F,
                   ISB=F,
                   ind = T)
```

##### Parametrization IV

```{r}
summary(hybrid_control_model_1_A_IV_cs)
MCMCvis::MCMCtrace(hybrid_control_model_1_A_IV_cs,
                   params=c('alpha','beta','tau'), 
                   type = 'density',
                   iter=990000,
                   pdf = F,
                   ISB=F,
                   ind = T)
MCMCvis::MCMCtrace(hybrid_control_model_1_A_IV_cs,
                   params=c('alpha','beta','tau'), 
                   iter=990000,
                   type = 'trace',
                   pdf = F,
                   ISB=F,
                   ind = T)
```

#### Model 2

```{r}
summary(hybrid_control_model_2_A_cs)
MCMCvis::MCMCtrace(hybrid_control_model_2_A_cs,
                   params=c('alpha','beta','tau'), 
                   type = 'density',
                   iter=990000,
                   pdf = F,
                   ISB=F,
                   ind = T)
MCMCvis::MCMCtrace(hybrid_control_model_2_A_cs,
                   params=c('alpha','beta','tau'), 
                   iter=990000,
                   type = 'trace',
                   pdf = F,
                   ISB=F,
                   ind = T)
```

#### Model 3
```{r}
summary(hybrid_control_model_3_A_cs)
MCMCvis::MCMCtrace(hybrid_control_model_3_A_cs,
                   params=c('alpha','beta','tau'), 
                   type = 'density',
                   iter=990000,
                   pdf = F,
                   ISB=F,
                   ind = T)
MCMCvis::MCMCtrace(hybrid_control_model_3_A_cs,
                   params=c('alpha','beta','tau'), 
                   iter=990000,
                   type = 'trace',
                   pdf = F,
                   ISB=F,
                   ind = T)
```

#### Model 4

```{r}
summary(hybrid_control_model_4_A_cs)
MCMCvis::MCMCtrace(hybrid_control_model_4_A_cs,
                   params=c('alpha','beta','tau'), 
                   type = 'density',
                   iter=990000,
                   pdf = F,
                   ISB=F,
                   ind = T)
MCMCvis::MCMCtrace(hybrid_control_model_4_A_cs,
                   params=c('alpha','beta','tau'), 
                   iter=990000,
                   type = 'trace',
                   pdf = F,
                   ISB=F,
                   ind = T)
```

### Population B (Flatiron atezo meeting inclusion criteria){.tabset .tabset-pills .tabset-fade}

#### Model 1

```{r}
summary(hybrid_control_model_1_B_cs)
MCMCvis::MCMCtrace(hybrid_control_model_1_B_cs,
                   params=c('alpha','beta','tau'), 
                   type = 'density',
                   iter=990000,
                   pdf = F,
                   ISB=F,
                   ind = T)
MCMCvis::MCMCtrace(hybrid_control_model_1_B_cs,
                   params=c('alpha','beta','tau'), 
                   iter=990000,
                   type = 'trace',
                   pdf = F,
                   ISB=F,
                   ind = T)
```

#### Model 2

```{r}
summary(hybrid_control_model_2_B_cs)
MCMCvis::MCMCtrace(hybrid_control_model_2_B_cs,
                   params=c('alpha','beta','tau'), 
                   type = 'density',
                   iter=990000,
                   pdf = F,
                   ISB=F,
                   ind = T)
MCMCvis::MCMCtrace(hybrid_control_model_2_B_cs,
                   params=c('alpha','beta','tau'), 
                   iter=990000,
                   type = 'trace',
                   pdf = F,
                   ISB=F,
                   ind = T)
```


#### Model 3

```{r}
summary(hybrid_control_model_3_B_cs)
MCMCvis::MCMCtrace(hybrid_control_model_3_B_cs,
                   params=c('alpha','beta','tau'), 
                   type = 'density',
                   iter=990000,
                   pdf = F,
                   ISB=F,
                   ind = T)
MCMCvis::MCMCtrace(hybrid_control_model_3_B_cs,
                   params=c('alpha','beta','tau'), 
                   iter=990000,
                   type = 'trace',
                   pdf = F,
                   ISB=F,
                   ind = T)
```

#### Model 4

```{r}
summary(hybrid_control_model_4_B_cs)
MCMCvis::MCMCtrace(hybrid_control_model_4_B_cs,
                   params=c('alpha','beta','tau'), 
                   type = 'density',
                   iter=990000,
                   pdf = F,
                   ISB=F,
                   ind = T)
MCMCvis::MCMCtrace(hybrid_control_model_4_B_cs,
                   params=c('alpha','beta','tau'), 
                   iter=990000,
                   type = 'trace',
                   pdf = F,
                   ISB=F,
                   ind = T)
```