---
title: "Summary of analyses"
subtitle: "Last updated `r Sys.Date()`"
author: "Artemis Koukounari, Matt Secrest (alphabetical)"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    keep_md: FALSE
---

```{r setup,include = FALSE}
knitr::opts_chunk$set(eval = TRUE,         # Evaluate code
                      echo = FALSE,         # echo code?
                      message = FALSE,     # Show messages
                      warning = FALSE,     # Show warnings
                      fig.width = 5,       # Default plot width
                      fig.height = 3,      # .... height
                      dpi = 300,           # Plot resolution
                      fig.align = "left")  # Figure alignment 
```

## Full results{.tabset .tabset-pills .tabset-fade}
### MORPHEUS-only population

#### Table

```{r}
morpheus_only_results_out[[1]]
```

#### Plot
```{r}
morpheus_only_results_out[[2]]

```


### Full population (including all RWD patients meeting inclusion/exclusion criteria)

No random effects modeling for the moment.

#### Table

```{r}
full_population_results_out[[1]]
```

#### Plot
```{r}
full_population_results_out[[2]]
```

### 1:1 PS matched population (including all RWD patients meeting inclusion/exclusion criteria)

#### Table

```{r}
matched_1_1_non_dynamic_results_out[[1]]
```

#### Plot
```{r}
matched_1_1_non_dynamic_results_out[[2]]
```

### Bayesian dynamic borrowing (1:1 PS matched population)

#### Table

```{r}
bdb_summary_matched_population_out[[1]]
```

#### Plot
```{r}
bdb_summary_matched_population_out[[2]]
```

### Bayesian dynamic borrowing (full population)

#### Table

```{r}
bdb_summary_full_population_out[[1]]
```

#### Plot
```{r}
bdb_summary_full_population_out[[2]]
```


## Select results

### Table

```{r}
succinct_summary_table
```


### Plot

```{r,fig.dim=c(10,5)}
succinct_summary_plot
```